%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Cies Resume/CV
% LaTeX Template
% Version 1.1 (20/7/14)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Cies Breijs (cies@kde.nl)
% https://github.com/cies/resume with extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt,a4paper]{article} % Font size (10-12pt) and paper size (a4paper, letterpaper, legalpaper, etc)

\include{structure} % Include structure.tex which contains packages and document layout definitions

\hyphenation{Some-long-word} % Specify custom hyphenation points in words with dashes where you would like hyphenation to occur, or alternatively, don't put any dashes in a word to stop hyphenation altogether

\begin{document} 

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\maintitle{Nathaniel Schultz}{}  % Your name and date of birth or subtitle

\noindent\href{mailto:nate.schultz@outlook.com}{nate.schultz@outlook.com}\bull % Your email address
\textsmaller{+}1 (978) 201-2997\bull % Your phone number(s) and Skype username
\href{https://github.com/beefy}{Github} \bull \href{https://www.linkedin.com/in/beefybeefy/}{Linkedin}\\ % Your URL
430 W Jefferson St, Apt 3\bull Philadelphia PA, 19122% Your address

\spacedhrule{0.9em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after

%----------------------------------------------------------------------------------------
%	SUMMARY SECTION
%----------------------------------------------------------------------------------------

% \roottitle{Summary} % Root section title

% \vspace{-1.3em} % Reduce whitespace after the Summary heading and the two-column content

% \begin{multicols}{2}  % Start a two-column layout
% \noindent \textit{A summary of your interests, achievements, history, topic of study or any other short summary of your professional life.}\\\\
% Lorem ipsum dolor sit amet, consectetur adipiscing elit. Nunc iaculis scelerisque vestibulum. Sed ut sapien et dui mollis condimentum. Phasellus enim lectus, dignissim vitae velit sit amet, porttitor tincidunt lectus. Vivamus adipiscing volutpat lacinia. Sed dui ipsum, iaculis id facilisis sed, dapibus quis lacus. Quisque blandit hendrerit malesuada. Nunc sollicitudin nisl nunc, vitae luctus leo tincidunt vel.

% Pellentesque bibendum convallis adipiscing. Suspendisse facilisis id massa a lacinia. Nullam odio nibh, placerat at fermentum in, tincidunt eu ipsum. Nullam adipiscing lacus id dui suscipit commodo. Vestibulum iaculis leo imperdiet, porta lorem eu, tempus tortor. Donec interdum risus ullamcorper, vestibulum nulla ut, tincidunt ante. Duis adipiscing auctor nisi, quis tempor tortor ornare aliquet. Aenean at tempor leo. Nam eleifend venenatis elit id aliquet. Mauris quis lacinia dolor, a posuere tellus. Suspendisse nec augue pretium, condimentum risus vitae, dignissim tellus. Proin gravida ante eget massa lacinia consequat. Integer pharetra vel ligula sed vulputate. Integer eget erat quam. Proin adipiscing lorem ac purus adipiscing, non ullamcorper nisi porttitor. 
% \end{multicols}

\spacedhrule{0.5em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after

%----------------------------------------------------------------------------------------
%	EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\roottitle{Recent Experience} % Top level section

\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{Bloomberg LP}
{\textsc{Princeton, NJ \& Philadelphia, PA (Remote)}} {

\headedsubsection % Job title entry for the current employer
{Acquisition Tech Lead}
{Dec '19 -- Present}
{\bodytext{As one of the initial members of this team, I gained ownership of implementing the team's technical projects. Our team is responsible for maintaining hundreds of thousands of web crawlers and increasing our coverage with new crawlers. I build platforms to add transparency and improve reporting for Bloomberg's acquisition processes. My project portfolio includes:\begin{itemize}  
 \item{A validation workflow with over 70 logic checks to ensure web crawlers are configured properly}
 \item{A full stack website to parse web crawler configurations for easier reporting}
 \item{A metadata triple store to link various acquisition databases together}
\end{itemize}

I also manage our co-op program, which is an important part of our hiring pipeline. I'm responsible for organizing our co-op hiring, on-boarding, and events. We have 4 co-ops that rotate biannually, across 4 different teams within the department.
}}

\headedsubsection % Job title entry for the current employer
{Data Engineer}
{Jun '19 -- Dec '19}
{\bodytext{In this role I contributed to several projects, managed our team's web crawler queue and oversaw our team's co-op. I worked on various microservices and a script to migrate and consolidate data from 3 legacy databases. I lead a project with three co-ops during this period to migrate the manual Jira access queue into our internal permission system.
}}

\headedsubsection % Job title entry for the current employer
{Data Engineer Co-Op}
{Apr '18 -- Sept '18}
{\bodytext{As the only co-op at the firm during this period, I was able to gain expertise in each tech stack component. My contributions during this period include web crawler configurations, microservice development, Jira workflow configuration, and productivity data EDA. I enjoyed hosting office activities like chess tournaments and weekly trivia.}}
}

%----------------------------------------------------------------------------------------
%	Other Experience
%----------------------------------------------------------------------------------------

\roottitle{Intern Experience} % Top level section

\headedsubsection % Job title entry for the current employer
{Booksmart Touring: Backend Engineer}
{July '16 -- Sept '17}
{\bodytext{\begin{itemize}  
 \item{Webserver Development: Python backend for a web and mobile application used by tour owners and musicians}
 \item{Specification Writing: Designed new feature implementations, considering scalability and maintainability.
Working with management and user interface teams to meet requirements.}
 \item{Data Management: Migrating data safely to new models, preserving data integrity and backwards compatibility
whenever possible.}
\end{itemize}}}

\headedsubsection % Job title entry for the current employer
{Chess.com: Software Developer Intern}
{March '17 -- May '17}
{\bodytext{\begin{itemize}  
 \item{Full Stack Feature Development: Developed and integrated a new feature for a website with millions of users.}
 \item{Testing: Found a production bug and developed a fix in python.}
\end{itemize}}}

\headedsubsection % Job title entry for the current employer
{Drexel Hyperloop: Control Systems Software Engineer}
{July '16 -- Oct '16}
{\bodytext{\begin{itemize}  
 \item{Sensor Data Logging: Implemented a database for live data streaming. Data sources from various engineering
systems were monitored for irregularities and performance.}
 \item{Requirements Coordination: Determined software needs of multiple teams, totaling over one hundred
personnel.}
\end{itemize}}}

\headedsubsection % Job title entry for the current employer
{Thomson Reuters, IP \& Science: Data Analyst}
{March '16 -- Sept '16}
{\bodytext{\begin{itemize}  
 \item{Big Data: Queried a Hadoop cluster to extract bibliometric data for customers. Optimized queries to deliver
results timely and inexpensively.}
 \item{Data Cleaning: Parsed files into a desired format. Added custom analytic fields.}
 \item{Web Scraping: Started data population for new features and data models.}
\end{itemize}}}

\headedsubsection % Job title entry for the current employer
{Armada International Advisors: Full Stack App Developer}
{Oct '14 -- Oct '15}
{\bodytext{\begin{itemize}  
 \item{IoT Project Development: Independently developed a medical equipment tracking application using Texas
Instruments’ sensors.}
 \item{Web and Mobile App Development: Developed and maintained multiple web and mobile apps.}
 \item{Web Scraping for Sales Leads: Collected contact information from potential clients using web crawlers and
social media scraping.}
\end{itemize}}}

%----------------------------------------------------------------------------------------

%------------------------------------------------


%------------------------------------------------


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\roottitle{Education} % Top level section

\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{Drexel University}
{\textsc{Philadelphia, PA}} {

\headedsubsection % Job title entry for the current employer
{Bachelor of Science in Computer Science}
{Sep '15 -- Jun '19}
{\bodytext{Focused on computational mathematics and artificial intelligence / machine learning. During this time I was employed at startups, participated in hackathons, and held membership in industry specific clubs. I've curated a diverse portfolio of programming projects including IoT, full stack mobile and web apps \textit{(hybrid and native)}, data analysis, graphics, and web crawlers.}}
}

%----------------------------------------------------------------------------------------
%	SKILLS SECTION
%----------------------------------------------------------------------------------------

\roottitle{Skills} % Top level section

%------------------------------------------------

\inlineheadsection % Special section that has an inline header with a 'hanging' paragraph
{Leadership:}
{Establishing relationships with engineering groups, business stakeholders, and peers. Solid communication and presentation skillset. Intern management and hiring experience. Skilled in vendor management and productivity data analysis.}

%------------------------------------------------

\inlineheadsection % Special section that has an inline header with a 'hanging' paragraph
{Technical:}
{Software design, workflow design, and data pipeline design. I work regularly with Python, Javascript, and Lua. Solid knowledge of web technologies and best practices relating to web crawling. Recent web development experience with React-Redux, Flask, SQL Alchemy, and PostgreSQL. CI experience with Docker and Docker-Compose. Data analysis experience in Python using Jupyter, Pandas, and Matplotlib.}

%------------------------------------------------

\inlineheadsection % Special section that has an inline header with a 'hanging' paragraph
{Mathematics:}
{Applied optimization theory to solve industrial design problems. Studied abstract algebra, analysis, statistics, and nonlinear algebra \textit{(among other topics).}}


\roottitle{Technology} % Top level section
Rubric (from worst to best): Novice, Advanced Beginner, Competent, Proficient, Expert
\inlineheadsection % Special section that has an inline header with a 'hanging' paragraph
{Languages:}
{Python (Proficient), Javascript (Competent), Lua (Advanced Beginner), Java (Competent), C# (Competent), C++ (Advanced Beginner), Go (Novice), VB (Novice), Objective-C (Novice), Haskell (Novice), Prolog (Novice)}
\inlineheadsection % Special section that has an inline header with a 'hanging' paragraph
{Backend Frameworks:}
{Flask (Proficient), FastAPI (Proficient), Django (Proficient), Express (Competent), Spring (Advanced Beginner), ASP.NET (Advanced Beginner)}
\inlineheadsection % Special section that has an inline header with a 'hanging' paragraph
{Frontend Frameworks:}
{React (Competent), Redux (Competent), Vue.js (Advanced Beginner), Android Native (Advanced Beginner), Bootstrap (Novice)}
\inlineheadsection % Special section that has an inline header with a 'hanging' paragraph
{Databases:}
{Apache Kafka (Proficient), MongoDB (Competent), MS SQL (Competent), mySQL (Competent), PostgreSQL (Competent), HiveQL (Advanced Beginner), Solr (Advanced Beginner), RDF Triplestore / SPARQL (Advanced Beginner)}

\spacedhrule{1.6em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after

\roottitle{Side Projects} % Top level section
\inlineheadsection
{One-way Anonymous Messaging App:}
{Native Android app to send and receive messages from strangers.}
\inlineheadsection
{Custom Garbage Collector:}
{Mark and sweep memory allocation example in Objective-C.}
\inlineheadsection
{Command Line Chess Server:}
{Real time chess as a simple networking example.}
\inlineheadsection
{Custom Graphics Engine:}
{ Features include VBO rendering, first person movement, and basic collision detection.}

\roottitle{Armchair Philosophy} % Top level section
\inlineheadsection
{Taoism and Monism:}
{Presocratic philosophers thought all life and matter was interconnected. Many-worlds quantum physicists believe our dimension is connected to other dimensions through a single [probability] wave function.}
\inlineheadsection
{Eternalism and Presentism:}
{Einstein's theory of relativity implies the existence of block-time, and that we only feel like we're in the present because every moment of time would feel like the present. Personally, I'm ontologically eternalist but epistemologically presentist.}
\inlineheadsection
{Free Will and Determinism:}
{Quantum indeterminacy can be resolved with either the many-worlds philosophy or with pilot wave theory. However, preservation of quantum information may not imply that free will cannot exist. The Heisenberg uncertainty principle implies that a system cannot be perfectly observed / predicted.}


%------------------------------------------------

\spacedhrule{1.6em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\roottitle{Activities} % Top level section

\inlineheadsection % Special section that has an inline header with a 'hanging' paragraph
{Hackathons:}
{Philly Codefest, Bitcamp, Numenta NuPic, Hackster.IO Hardware Weekend, PSU Hacks}
\inlineheadsection % Special section that has an inline header with a 'hanging' paragraph
{Clubs:}
{Bloomberg Toastmasters VP of Membership, Drexel Chess Club President, LaEsquina Garden Member}

\roottitle{Interests} % Top level section

\inlineheadsection % Special section that has an inline header with a 'hanging' paragraph
{Non-exhaustive and in alphabetical order:}
{Buddhism, camping, chess, DeFi, mathematics, open source, philosophy, Rubik's cubes, software engineering, vegetarian cooking, volunteering, and yoga.}

%----------------------------------------------------------------------------------------

\end{document}
